---
title: "Interesting R Examples"
author: Gokhan Sahin - BDA 503 - Fall 2017
---

```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```
###1)[Forest Fires Data Set](https://archive.ics.uci.edu/ml/datasets/forest+fires)
 In [Cortez and Morais, 2007], the output 'area' was first transformed with a ln(x+1) function. 
Then, several Data Mining methods were applied. After fitting the models, the outputs were 
post-processed with the inverse of the ln(x+1) transform. Four different input setups were 
used. The experiments were conducted using a 10-fold (cross-validation) x 30 runs. Two 
regression metrics were measured: MAD and RMSE. A Gaussian support vector machine (SVM) fed 
with only 4 direct weather conditions (temp, RH, wind and rain) obtained the best MAD value: 
12.71 +- 0.01 (mean and confidence interval within 95% using a t-student distribution). The 
best RMSE was attained by the naive mean predictor. An analysis to the regression error curve 
(REC) shows that the SVM model predicts more examples within a lower admitted error. In effect, 
the SVM model predicts better small fires, which are the majority.
```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/Users/berkorbay/Dropbox/Courses_given/MEF_BDA_503_2017F/Guidelines/example_homework_1.Rmd",output_format="pdf_document")
rmarkdown::render("/Users/berkorbay/Dropbox/Courses_given/MEF_BDA_503_2017F/Guidelines/example_homework_1.Rmd",output_format="html_document")
```


###2)[Gas sensor array under flow modulation Data Set](http://archive.ics.uci.edu/ml/datasets/Gas+sensor+array+under+flow+modulation) 


This data set contains 13,910 measurements from 16 chemical sensors exposed to 6 gases at different concentration levels. This dataset is an extension of the Gas Sensor Array Drift Dataset ([Web Link]), providing now the information about the concentration level at which the sensors were exposed for each measurement. The primary purpose of making this dataset freely accessible on-line is to provide an extensive dataset to the sensor and artificial intelligence research communities to develop and test strategies to solve a wide variety of tasks, including sensor drift, classification, regression, among others. 

The dataset can be used exclusively for research purposes. Commercial purposes are fully excluded. Citation of both Vergara et al. 'Chemical gas sensor drift compensation using classifier ensembles' and Rodriguez-Lujan et al. “On the calibration of sensor arrays for pattern recognition using the minimal number of experiments” is required (see below). 

The dataset was gathered during the period of January 2008 to February 2011 (36 months) in a gas delivery platform facility situated at the ChemoSignals Laboratory in the BioCircuits Institute, University of California San Diego. The measurement system platform provides versatility for obtaining the desired concentrations of the chemical substances of interest with high accuracy and in a highly reproducible manner, minimizing thereby the common mistakes caused by human intervention and making it possible to exclusively concentrate on the chemical sensors. See reference 1 for more details on the experimental setup. 

The resulting dataset comprises recordings from six distinct pure gaseous substances, namely Ammonia, Acetaldehyde, Acetone, Ethylene, Ethanol, and Toluene, dosed at a wide variety of concentration levels in the intervals (50,1000), (5,500), (12,1000), (10,300), (10,600), and (10,100) ppmv, respectively.

###3)[Heart Disease](http://archive.ics.uci.edu/ml/datasets/Heart+Disease)

This database contains 76 attributes, but all published experiments refer to using a subset of 14 of them. In particular, the Cleveland database is the only one that has been used by ML researchers to 
this date. The "goal" field refers to the presence of heart disease in the patient. It is integer valued from 0 (no presence) to 4. Experiments with the Cleveland database have concentrated on simply attempting to distinguish presence (values 1,2,3,4) from absence (value 0). 

The names and social security numbers of the patients were recently removed from the database, replaced with dummy values. 

One file has been "processed", that one containing the Cleveland database. All four unprocessed files also exist in this directory. 

To see Test Costs (donated by Peter Turney), please see the folder "Costs"


###4)[Madelon Data Set ](http://archive.ics.uci.edu/ml/datasets/Madelon)

MADELON is an artificial dataset containing data points grouped in 32 clusters placed on the vertices of a five dimensional hypercube and randomly labeled +1 or -1. The five dimensions constitute 5 informative features. 15 linear combinations of those features were added to form a set of 20 (redundant) informative features. Based on those 20 features one must separate the examples into the 2 classes (corresponding to the +-1 labels). We added a number of distractor feature called 'probes' having no predictive power. The order of the features and patterns were randomized. 

###5)[Mushroom Data Set  ](http://archive.ics.uci.edu/ml/datasets/Mushroom)

This data set includes descriptions of hypothetical samples corresponding to 23 species of gilled mushrooms in the Agaricus and Lepiota Family (pp. 500-525). Each species is identified as definitely edible, definitely poisonous, or of unknown edibility and not recommended. This latter class was combined with the poisonous one. The Guide clearly states that there is no simple rule for determining the edibility of a mushroom; no rule like ``leaflets three, let it be'' for Poisonous Oak and Ivy.
