---
title: "HR Analytics"
utput: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction 
This dataset is simulated  <br/>
* Fields in the dataset include: <br/>
* Employee satisfaction level (satisfaction_level) <br/>
* Last evaluation (last_evaluation) <br/>
* Number of projects (number_project) <br/>
* Average monthly hours (average_montly_hours) <br/>
* Time spent at the company (time_spend_company) <br/>
* Whether they have had a work accident (Work_accident) <br/>
* Whether they have had a promotion in the last 5 years <br/> (promotion_last_5years)
* Sales (sales) <br/>
* Salary (salary) <br/>
* Whether the employee has left (left) <br/>

```{r, echo=F, message=F, warning=F}
hr = read.table('D:/HR_comma_sep.csv', header = T,sep=',')
```



```{r}
str(hr)

```

```{r, echo=F, message=F, warning=F}

library('tidyverse')

SM_last_evaluation <-hr %>% group_by(salary)  %>% summarise(Average_last_evaluation=mean(last_evaluation))

ggplot(data=SM_last_evaluation,aes(x=salary,y=Average_last_evaluation)) + geom_bar(stat="identity",fill="#00FF84")


```

```{r}
montly_hours <-hr %>% group_by(salary)  %>% summarise(Sum_Montly_Hours=sum(average_montly_hours))

ggplot(data=montly_hours,aes(x=salary,y=Sum_Montly_Hours)) + geom_bar(stat="identity",fill="#00FF84")

```

```{r}
SM_satisfaction_level <-hr %>% group_by(sales)  %>% summarise(sumsales=mean(satisfaction_level))

ggplot(data=SM_satisfaction_level,aes(x=sales,y=sumsales)) + geom_bar(stat="identity",fill="#00FF84")
```












