---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```






# Introduction 
This dataset is simulated  <br/>
* Fields in the dataset include: <br/>
* Employee satisfaction level (satisfaction_level) <br/>
* Last evaluation (last_evaluation) <br/>
* Number of projects (number_project) <br/>
* Average monthly hours (average_montly_hours) <br/>
* Time spent at the company (time_spend_company) <br/>
* Whether they have had a work accident (Work_accident) <br/>
* Whether they have had a promotion in the last 5 years <br/> (promotion_last_5years)
* Sales (sales) <br/>
* Salary (salary) <br/>
* Whether the employee has left (left) <br/>

```{r, echo=F, message=F, warning=F}
hr = read.table('D:/HR_comma_sep.csv', header = T,sep=',')
```


```{r, echo=F, message=F, warning=F}
# Library needed:
str(hr)
```



```{r , fig.width=4, fig.height=4}
hr$sales<-as.factor(hr$sales)
hr$salary<-as.factor(hr$salary)
hr$salary<-ordered(hr$salary,levels=c("low","medium","high"))
```

```{r , fig.width=4, fig.height=4}
library(corrplot)
cor(hr[,1:8])
corrplot(cor(hr[,1:8]), method="circle")
```








